Simple repression draft

### 2020-05-21 doc/abstract.tex

% !TEX root = ./busty_transcription.tex
\begin{abstract}
Abstract here.
\end{abstract}

>>>>

% !TEX root = ./busty_transcription.tex
\begin{abstract}
The study of transcription remains one of the centerpieces of modern biology
with implications in settings from development to metabolism to evolution to
disease. Precision measurements using a host of different techniques including
fluorescence and sequencing readouts have raised the bar for what it means to
quantitatively understand transcriptional regulation. In particular our
understanding of the simplest genetic circuit is sufficiently refined both
experimentally and theoretically that it has become possible to carefully
discriminate between different conceptual pictures of how this regulatory system
works. This regulatory motif, originally posited by Jacob and Monod in the
1960s, consists of a single transcriptional repressor binding to a promoter site
and inhibiting transcription. In this paper, we show how seven distinct models
of this so-called simple-repression motif, based both on equilibrium and kinetic
thinking, can be used to derive the predicted levels of gene expression. These
different models are invoked to confront a variety of different data on mean,
variance and full gene expression distribution, illustrating the extent to which
such models can be distinguished.
\end{abstract}

### 2020-05-21 doc/appendix_02_constitutive_promoters.tex

% !TEX root = ./busty_transcription.tex
\section{Derivations of constitutive promoter models}
\subsection{Model 2}
\mmnote{Obtain Fano factor from CME.}
\subsection{Model 3}
\mmnote{Obtain Fano factor by taking limit from Mitarai et al's expression.}
\subsection{Model 4}
\mmnote{Obtain Fano factor by relabeling cartoon from Jones2014.}

>>>>

% !TEX root = ./busty_transcription.tex
\section{Derivations for non-bursty promoter models}
\subsection{Nonequilibrium Model One - Poisson Promoter}
\mmnote{Derive mean mRNA referred to in means section.}

\subsection{Nonequilibrium Model Two - RNAP Bound and Unbound States}
\mmnote{Obtain mean mRNA and Fano factor from CME.}

\subsection{Nonequilibrium Model Three
    - Multistep Transcription Initiation and Escape}
\mmnote{Derive mean mRNA from CME.}
\newline
\mmnote{Obtain Fano factor by taking limit from Mitarai et al's expression.}

\subsection{Nonequilibrium Model Four
    - ``Active'' and ``Inactive'' States}
\mmnote{Derive mean mRNA from CME.}
\newline
\mmnote{Obtain Fano factor by relabeling cartoon from Jones2014.}
